### 2016-09-28 R/ITHIM.Rmd
Removed update of pWalk
pWalk is now calculated using mean times

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
upper <- 25; wd <- 1; length <- upper/wd + 1;

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIM.default, "pWalk", 0.85)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)

>>>>

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
upper <- 25; wd <- 10; length <- upper/wd + 1;

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)
